Co-moving stars in \textsl{Gaia DR1}

### 2016-11-09 paper/ms.tex
tweak in figure captions

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/graphviz_examples.pdf}
  \end{center}
  \caption{%
    Visualizations of a few example networks of co-moving pairs of stars.
    Each star (node) is marked as red circles, and a line (edge) is drawn
    between two stars if they are co-moving by our selection criteria
    (see \S~\ref{sub:selection}). On left, we show the largest network
    found in this study corresponding to the Pleiades star cluster.
    \label{fig:graphviz_examples}}
\end{figure*}

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/glon_d_pie.pdf}
  \end{center}
  \caption{%
    Panoramic view of co-moving pairs of stars. The angle is the Galactic
    longitude, and the distance is in pc.
    Pair networks of sizes less 6 are connected by gray lines.
    Pair networks of size larger than 6 are plotted with a unique color per network.
    We also show the positions of known Milky Way star clusters
    from \citet{Kharchenko:2016aa} as empty purple circles,
    and stars in OB associations from \citet{de-Zeeuw:1999aa} as
    black circles.
    \label{fig:glon_d_pairlines}}
\end{figure*}

@@

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/gjg_graphviz_examples.png}
  \end{center}
  \caption{
    Color-magnitude diagrams of stars in larger networks presented in
    Figure~\ref{fig:graphviz_examples}. Each panel corresponds to the panel
    at the same position in Figure~\ref{fig:graphviz_examples}.
    We show the distribution of all stars common in \tgas\ and \tmass\
    with parallax $S/N>16$ in blue for reference.
    \label{fig:cmd_large}}
\end{figure*}

>>>>

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/graphviz_examples.pdf}
  \end{center}
  \caption{%
    Visualizations of a few example networks of co-moving pairs of stars.
    Each star (node) is marked as a red circle, and a line (edge) is drawn
    between two stars if they are co-moving by our selection criteria
    (see \S~\ref{sub:selection}). On left, we show the largest network
    found in this study corresponding to the Pleiades star cluster.
    \label{fig:graphviz_examples}}
\end{figure*}

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/glon_d_pie.pdf}
  \end{center}
  \caption{%
    Panoramic view of co-moving pairs of stars. The angle is the Galactic
    longitude, and the distance is in pc.
    Pair networks of sizes less than 5 are connected by gray lines.
    Pair networks of size $\geq 5$ are plotted with a unique color per network.
    We also show the positions of known Milky Way star clusters
    from \citet{Kharchenko:2016aa} as empty purple circles,
    and stars in OB associations from \citet{de-Zeeuw:1999aa} as
    black circles.
    \label{fig:glon_d_pairlines}}
\end{figure*}

@@

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/gjg_graphviz_examples.png}
  \end{center}
  \caption{
    Color-magnitude diagrams of stars in larger networks presented in
    Figure~\ref{fig:graphviz_examples}. Each panel shows the same network
    visualized in the panel at the same position
    in Figure~\ref{fig:graphviz_examples}.
    We show the distribution of all stars common in \tgas\ and \tmass\
    with parallax $S/N>16$ in blue for reference.
    \label{fig:cmd_large}}
\end{figure*}
